Secondary analysis of tables

### 2019-08-26 Analysis/Category_Tables.Rmd
Convert tables to match text

Disease_Sum = read.csv("../manuscript/tables/supplementary_table_S1.csv")

@@

saveWorkbook(wb, "../manuscript/tables/Supplementary_Table_S1.xlsx")

@@

write.csv(Cat_Within, "../manuscript/tables/Table_1.csv", row.names = FALSE)
```

>>>>

Disease_Sum = read.csv("../manuscript/tables/supplementary_table_S3.csv")

@@

saveWorkbook(wb, "../manuscript/tables/supplementary_table_S1.xlsx")

@@

write.csv(Cat_Within, "../manuscript/tables/table_1.csv", row.names = FALSE)
```

### 2019-08-26 manuscript/Analysis_Tables_New.Rmd
Convert tables to match text

fileNameIn0  <- "tables/supplementary_table_S1.csv"   # diseases and traits, coherence new KEGG, REACTOME, CC. 2019-07-14, Kellen
# iconv -f UTF-8 -t ISO-8859-1 -c supplementary_table_S1.csv > tmp.csv
mtx0 <- read_csv(fileNameIn0) %>% as.data.frame()
rownames(mtx0) <- mtx0$Disease
```

>>>>

fileNameIn0  <- "tables/supplementary_table_S3.csv"   # diseases and traits, coherence new KEGG, REACTOME, CC. 2019-07-14, Kellen
# iconv -f UTF-8 -t ISO-8859-1 -c supplementary_table_S3.csv > tmp.csv
mtx0 <- read_csv(fileNameIn0) %>% as.data.frame()
rownames(mtx0) <- mtx0$Disease
```
